---
title: "Course resources"
description: |
  Here are key course documents and resources, ranging from the syllabus to software help.
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Essential course information

- Syllabus

- Problem topic sheet

- Specifications for successful work


## Textbook

The required textbook is *Probability and Bayesian Modeling* by Jim Albert and Monika (Jingchen) Hu (2020, CRC).

A free ebook version is available here: https://bayesball.github.io/BOOK/


## Software installation

### R/RStudio

We will use R/RStudio as our computational engine. Please install the current version of R and RStudio at the beginning of the term if you plan to use a local version.

Download R: https://cran.r-project.org/

Download RStudio desktop: https://www.rstudio.com/products/rstudio/download/#download

The maize server (https://maize.mathcs.carleton.edu) is also available for your use, but can only be accessed on campus of via a VPN.

### JAGS

We will use JAGS (Just Another Gibbs Sampler) "automate" some of the posterior sampling via MCMC this term. Please install JAGS using prior to installing the R packages listed below.

Link to the latest version: https://sourceforge.net/projects/mcmc-jags/files/latest/download


### R packages

We will use numerous R packages throughout this course. They are all installed on the maize R Studio server. If you are working on a local install, then please run the code chunk below to install all of the packages. I recommend doing this at the beginning of the course to avoid last minute installation issues preventing you from completing assignments.

```{r eval=FALSE}
install.packages(c("ProbBayes", "loo", "coda", "runjags", "MCMCpack",
                   "tidybayes", "VGAM"), dependencies = TRUE)
```

