---
title: "Week 03: Means and counts"
description: |
  This week, we'll discuss Bayesian models for measurement and count data. 
  Specifically, well explore using the normal distribution with known variance for
  measurement data and the Poisson distribution for count data.
date: 09-27-2021
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 2
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Monday, 27 Sept

### Topics

Modeling measurement data

### Materials

[Slides](https://aloy.github.io/stat340-notes-fa21/06-normal-mean.pdf)

[Your turns](https://aloy.github.io/stat340-notes-fa21/06H-normal-mean-derive.pdf)

[Collaborative notes](https://docs.google.com/document/d/1rkwZ_b2R9ZiSzZ9CC2xE--sAq2Jjw5AVSmxogXwooB4/edit?usp=sharing)


### Before next time

1. Read sections 8.6-8.7

1. Work on homework 2



## Wednesday, 28 Sept

### Topics

- Posterior predictive for measurement data

- Modeling count data

### Materials

- First, We'll wrap up Monday's slides

- [Slides for count data](https://aloy.github.io/stat340-notes-fa21/07-poisson-count.pdf)

- [Your turns](https://aloy.github.io/stat340-notes-fa21/07H-poisson-example.pdf)

Here's the code to pull in the `gamma_solver()`:

```{r eval=FALSE, echo=TRUE}
devtools::source_gist("https://gist.github.com/aloy/9d0385363663a28bd8eccf85bf9475bf")
```



### Before next time

1. Finish homework 2 and upload to Gradescope before Friday's class

1. Read section 9.1



## Friday, 24 Sept

### Announcements

- Homework 2 is due by 9:40 am

- [Writing assignment 1 draft](https://www.dropbox.com/s/8o5xinuv0cnwp13/01-prior-tuning.pdf?dl=0) is due Monday by 9:50 am

- I will post Homework 3 today

- Exam 1 is Friday, October 8

### Topics

- Two-parameter normal model

- Grid approximation


### Materials

[Slides](https://aloy.github.io/stat340-notes-fa21/08-intro-multiparameter.pdf)

[R code handout](https://aloy.github.io/stat340-notes-fa21/08H-multiparameter.html)


### Before next time

1. Write [prior tuning draft](https://www.dropbox.com/s/8o5xinuv0cnwp13/01-prior-tuning.pdf?dl=0), submit this on Moodle for peer review

1. Start homework 3





